% TODO: makes wrapping line around less retarded
\documentclass[11pt]{res}
\newsectionwidth{0pt}
\usepackage[a4paper,bindingoffset=0.4in,%
  left=0.3in,right=0.5in,top=0.4in,bottom=0.3in,%
  footskip=.25in]{geometry}
\usepackage{tabto}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{hyperref}
\setmainfont{Linux Libertine O}
\usepackage[most]{tcolorbox}
\usepackage{color}

\newcommand{\sectionunderline}{\vspace{-3mm}\hrulefill\\}
\newcommand{\listingtab}{\tabto{3.5cm}}
\newcommand{\familiartab}{\tabto{6.7cm}}
\newcommand{\afterfamiliar}{\tabto{9.8cm}}
%\newcommand{\newsect}[1]{\section{\begin{tcolorbox}[adjusted title=flush center, halign=flush center, bicolor, colback=gray!20, frame hidden, boxrule=0pt, colbacklower=white] \Large \bf #1 \end{tcolorbox}}}
\newcommand{\newsect}[1]{\section{\Large \bf #1}}
\newcommand{\email}[1]{\faEnvelope\hspace{1mm} \href{mailto:#1}{#1}}
\newcommand{\phone}[1]{\faMobilePhone\hspace{1mm} #1}
\newcommand{\github}[1]{\faGithubAlt\hspace{1mm} \href{https://github.com/#1}{#1}}
\newcommand{\linkedin}[1]{\faLinkedinSquare\hspace{1mm} \href{https://linkedin.com/in/#1}{#1}}

\hypersetup{
  colorlinks=true,
  urlcolor=blue
}

\makeatletter
\def\@tablebox#1{\begin{tabular}[t]{@{}c@{\extracolsep{\fill}}}#1\end{tabular}}
\makeatother

\definecolor{darkgray}{gray}{0.15}

\begin{document}
\name{\Huge Derek Pham\\[5pt]}
\address{
  \large\phone{(802) 503-5089}\:
  \large{$\bullet$}
  \large\email{derekpham67@gmail.com}\:
  \large{$\bullet$}
  \large\github{derekpham}\:
  \large{$\bullet$}
  \large\linkedin{derek-pham97}\\
  \normalsize Availability for internships/co-ops: Jan. - Aug. 2020
}

\begin{resume}
  \newsect{\faGraduationCap\ EDUCATION}{
    \sectionunderline{
      {\bf Northeastern University}, Boston, MA \hfill Sept. 2016 - present\\
      College of Computer and Information Science}\\
                     {\it Candidate for a Bachelor of Science in Computer Science, Minors in Mathematics and Physics} \hfill Dec. 2020
                     \vspace{2mm}\\
                     GPA:\listingtab 3.97/4.0
  }

  \newsect{\faUsers\ EXPERIENCE}{
    \sectionunderline{
      {\bf Yelp}, San Francisco, CA \hfill Jun. 2019 - Aug. 2019\\
      {\it Sofware Engineer Intern - Data Metrics}
      \begin{itemize}
        {\item Creating a batch post-processor tool for Yelp's data lake, enabling better business decision making due to more accurate post-processed data}
        {\item Technologies used: Python, PySpark, AWS Glue, Amazon S3}
      \end{itemize}

      {\bf HubSpot}, Cambridge, MA \hfill Jan. 2019 - May. 2019\\
      {\it Software Developer Co-op - Connected Email Backend}
      \begin{itemize}
        {\item Migrated 2 Redis databases to HBase, saving around \$100,000 a year}
        {\item Redesigned the email scheduling ecosystem to incorporate  MySQL, HBase and Amazon S3, which solved 5 different bugs that caused painful and long-lasting Jiras}
        {\item Communicated with other teams to scope REST endpoints for approximately 10 different projects, improving security of HubSpot's APIs.}
        {\item Technologies used: Java, DropWizard, Hadoop, HBase, Kafka, MySQL}
      \end{itemize}

      {\bf Northeastern University}, Boston, MA \hfill Sept. 2017 - present\\
      {\it Research Assistant for Christo Wilson and Ron Robertson - Network Science Department}
      \begin{itemize}
        {\item Creating website in Django studying how search ranking affects personal and political opinions}
        {\item Designing application's entire SQLite database schema to store subjects' information}
        {\item Configuring application to assign each subject a random treatment of pre-ordered search results and track browsing activities}
        {\item Developing frontend with ability to switch between different CSS skins to mimic sites such as search sites, social media sites, and job posting sites}
        {\item Technologies used: Python, Django}
      \end{itemize}

      {\bf PowerAdvocate}, Boston, MA \hfill Jan. 2018 - Jun. 2018\\
      {\it Software Developer Co-op - Data As a Service Team}
      \begin{itemize}
        {\item Built upon and delivered completed product, Customer Service Report (CSR), shortening Customer Success team's time to produce reports by around 50 times}
        {\item Developed all required features virtually from scratch for 3 different kinds of reports, in Spring and Hibernate}
        {\item Researched database providers and chose CSR's database to be PostgreSQL}
        {\item Technologies used: Java, Spring, Hibernate, Gradle, PostgreSQL, Ansible}
      \end{itemize}
    }
  }

  \newsect{\faGithubAlt\ PROJECTS}{
    \sectionunderline{
      {\bf nualt} \hfill Ongoing\\
      {\it An easy-to-use alternative to Northeastern's career website}
      \begin{itemize}
        {\item \sloppy{Creating a browser extension in Javascript to extract information on every visited job page on Northeastern's career website (and potentially other job sites)}}
        {\item Building REST API to store and retrieve job information using Kotlin and Spring Boot}
        {\item Designing simple and easy-to-use front end in Javascript using jQuery and JsGrid}
      \end{itemize}
    }
  }
\end{resume}
\end{document}
